---
title: "Final Project"
author: "DI_LC_AZT"
date: "20/10/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Looking at power of experiment beforehand:
Assume:
$\mu_c = \dfrac{14}{21}$ meals for the week contain meat for the control group - Guess  
$\mu_t = \dfrac{11}{21}$ meals for the week contain meat for the treatment group - Guess    
$\sigma = \dfrac{2}{21}$ meals for the week std. dev. for treatment and control - Guess   
$N = 20$ number of total participants in block; half in control, half in treatment- Guess  
$\alpha = 0.05$ significance level  

From Gerber and Green, p. 93:  
$\beta = \Phi\left(\dfrac{|\mu_t-\mu_c|\sqrt{N}}{2\sigma}-\Phi^{-1}\left(1-\frac{\alpha}{2}\right)\right)$  

```{r}
# Textbook example - they get 80% power
mut <- 65
muc <- 60
sigma <- 20
N <- 500
alpha <- 0.05

cdf_inv <- qnorm(p=alpha/2, lower.tail=FALSE)
cdf_inv

normed <- ((mut-muc)*sqrt(N))/(2*sigma)
normed

q <- normed - cdf_inv

power <- pnorm(q)
power
```

```{r}
# Guesstimate at our power with one treatment effect
mut <- 14/21
muc <- 11/21
sigma <- 2/21
N <- 20
alpha <- 0.05

cdf_inv <- qnorm(p=alpha/2, lower.tail=FALSE)
cdf_inv

normed <- ((mut-muc)*sqrt(N))/(2*sigma)
normed

q <- normed - cdf_inv

power <- pnorm(q)
power
```


# Power of Full Experiment

Looking at power of experiment beforehand:
Assume:
$\mu_c = \dfrac{14}{21}$ meals for the week contain meat for the control group - Guess  
$\mu_t = \dfrac{11}{21}$ meals for the week contain meat for the treatment group - Guess    
$\sigma = \dfrac{2}{21}$ meals for the week std. dev. for treatment and control - Guess   
$N = 20$ number of total participants in block; half in control, half in treatment- Guess  
$\alpha = 0.05$ significance level  

From Gerber and Green, p. 93:  
$\beta = \Phi\left(\dfrac{|\mu_t-\mu_c|\sqrt{N}}{2\sigma}-\Phi^{-1}\left(1-\frac{\alpha}{2}\right)\right)$  


```{r}
# Guesstimate at our power with TWO treatment effects
mut <- 14/28
muc <- 11/28
sigma <- 2/28
N <- 27
alpha <- 0.05

cdf_inv <- qnorm(p=alpha/2, lower.tail=FALSE)
cdf_inv

normed <- ((mut-muc)*sqrt(N))/(2*sigma)
normed

q <- normed - cdf_inv

power <- pnorm(q)
power
```

