---
title: "Pilot_Preparation"
author: "DI_LC_AZT"
date: "04/11/2019"
output: 
    html_document: default
    pdf_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(
    inputFile, encoding = encoding,
    output_format = c('pdf_document')) 
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(blockTools)
library(data.table)
library(knitr)
```


# Import Data and Clean
- In Excel, changed headers of columns from question to short name
```{r}
rawdata <- read.csv('Pilot Enrollment Survey - Eating HabitsClean.csv')
dim(rawdata)
```

```{r}
str(rawdata)
```

```{r}
levels(rawdata$eatertype)
levels(rawdata$mealplanner)
levels(rawdata$allergy)
```



- Eliminate Rows where `eatertype` is `Vegetarian`, `Vegan` or `Pescatarian`, i.e. select only rows where eatertype is `Meat Eater` or `None of these`. In this case, not necessary, as there are only 2 factors in the respondents. Similarly we have 3 factor levels required for the mealplanner.

# Create Blocking and Treatment Variables

- Proportion of meat meals (1: >0-0.25, 2: >0.25-0.5, 3: >0.5-0.75, 4: 0.75-1)  
- Food Allergies present (1) or None (0)  
- Already created: Meal Planning Status (factor): (1: Not Relevant, 2: Shared responsibility, 3: Yes Main Planner)  

SO:  
- Adjust the allergy column, so that if it is 'None', it becomes 0 and all other values = 1   
- ConvertMealPlanner column from factors  
- Finally, calculate the proportion of meat meals and also create a factor column for the ranges  

AND:  
- create the treatremind, treatrecipe, control columns, and set all to 0  

```{r}
workingdt <- data.table(rawdata)
workingdt[,allergybinary:=0]
workingdt[allergy != 'None', allergybinary := 1]
workingdt[,propmeat:=meat/eatingoccasions ]
workingdt[,propmeatrange := 1] # set default value
workingdt[propmeat > 0.25 & propmeat <= 0.5, propmeatrange := 2]
workingdt[propmeat > 0.5 & propmeat <= 0.75, propmeatrange := 3]
workingdt[propmeat > 0.75 & propmeat <= 1.0, propmeatrange := 4]
workingdt[,c('treatremind','treatrecipe','control'):= 0]
workingdt$mealplanner <- as.numeric(workingdt$mealplanner)
```

# Do the Blocking

```{r}
out <- block(workingdt,n.tr=3,id.vars=c('phonenumber','Name'),
             block.vars=c("propmeatrange","allergybinary","mealplanner"),
             verbose=FALSE)
```
```{r}
out$blocks
```
# Resultant Blocks
From the above we can see that the 3 Treatment conditions: 'Unit 1', 'Unit 2' and 'Unit 3' are selected into 4 blocks - the rows.   

Must cite: Moore, Ryan T. and Keith Schnakenberg. "blockTools: Blocking, Assignment, and Diagnosing Interference in Randomized Experiments", Version 0.6-3, December 2016.  

and the papers:  

Moore, Ryan T. ``Multivariate Continuous Blocking to Improve Political Science Experiments''. Political Analysis, 20(4):460--479, Autumn 2012.   

Moore, Ryan T. and Sally A. Moore. ``Blocking for Sequential Political Experiments''. Political Analysis, 21(4):507–523, 2013.  

Now assign these numbers/treatments to the 3 columns in the workingdata table at random.  

```{r}
assigned <- assignment(out, namesCol=c('control','treatremind','treatrecipe'),seed=42)
outCSV(assigned)
```

Set this data back into the working data table - can't figure out how to get it out of the blocktools assignment object, so just sent to CSV and remiported it.  

```{r}
randomized <- data.table(read.csv('Group1.csv'))
randomized
```

```{r}
workingdt[phonenumber %in% randomized[,control], control:=1]
workingdt[phonenumber %in% randomized[,treatremind], treatremind:=1]
workingdt[phonenumber %in% randomized[,treatrecipe], treatrecipe:=1]
```

# Extract to send to Diana for texting

```{r}
assignments <- workingdt[,c("Name","phonenumber","treatremind","treatrecipe","control"),with=FALSE]
```

Export to CSV  

```{r}
write.csv(assignments,file='PilotAssignments.csv', row.names = FALSE)
```

# Extract Comments and export to CSV

```{r}
feedback <- workingdt[,c("feedback"),with=FALSE]
write.csv(feedback,file='PilotEnrollmentSurveyFeedback.csv')
```

